Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-23 ASA2013/asa2013.tex
la2pdf commit - 2013:01:23	03:41:09	(Wed23.Jan)

This article is outlined as follows: First we will present\todo{denne formuleringstypen begynner aa bli oppbrukt...} background material on the MVDR method operated in time and frequency domain, and on the LCA beamformer. For each method we start with the mathematical formulation, then evaluate complexity issues, and finally give our thoughts on some implementation aspects. The results are collected in \ref{implementation}. Finally, we conclude in section \ref{discssion}.

@@

A few properties let us improve these matters notably. First, we may infer from (\ref{spatialR}) that:
\begin{itemize}
\item The subarray covariance matrices $R_l[n] = \x_l[n]\x_l\H[n]$ are Hermitian semi-definite, which means that we can get away with computing only one triagonal in them.
\item When summing $R_l[n]$ most of the multiplications can be computed only once, and most sums need only be updated iteratively.
\end{itemize}
Second, each of the diagonals of $R_l[n]\ \forall\ l$ can be computed independently, which is good news for our GPU design.

@@

By reducing the covariance size from $L$ to $N_b$ we also reduce the estimation step to O($N_K N_L N_b^2$), and the inversion step to O($N_b^3$). The downside is the additional O[$N_b  Complexity: To\,L$) computations required  frequency domain: O($N_b\,L$). Build $R_\text{BS}$, O($N_b^2\,N_L\,N_K$), Inversion: O($N_b^3$).

@@

>>>>

This article is outlined as follows: First we will present the mathematical formulation and evaluate complexity aspects of the MVDR method operated in time or frequency domain, and on the LCA beamformer. Then we mention some of our experiences with implementing the MVDR on a GPU, before concluding with some results and final thoughts.

@@

A few properties let us improve these matters notably. First, we may infer from (\ref{spatialR}) that:
\begin{itemize}
\item The subarray covariance matrices $R_l[n] = \x_l[n]\x_l\H[n]$ are Hermitian semi-definite, which means that we can get away with computing only one triagonal in them.
\item When summing $R_l[n]$ most of the multiplications need only be computed only once, and most sums can be updated iteratively.
\end{itemize}
Second, each of the diagonals of $R_l[n]\ \forall\ l$ can be computed independently, which is good news for our GPU design.

@@

By reducing the covariance size from $L$ to $N_b$ we also reduce the estimation step to O($N_K N_L N_b^2$), and the inversion step to O($N_b^3$). Although the additional computations required by the frequency transform must be taken into consideration, the effect of adjusting far outweighs it for larger systems.

@@

Frequency domain MVDR beamforming
